Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-30 ms.tex
figures. yay!

The top panel of Figure~\ref{fig:stag} shows our results for the stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$, with different colors showing different values of $v_{w}$.  Cusp and core galaxies are marked with square and triangles, respectively.  Shown for comparison as a solid black line is the simplified analytic approximation for $r_{\rm s}$ from \eqref{eq:stag_simple}. For high $\vwO$ the analytic prediction agrees well with our numerical results. However, \eqref{eq:stag_simple} is only valid that $\Mstar|_{r_{\rm s}} \ll \Mbh$, and
this approximation breaks down for small $\vwO$. In fact, $\rs$
diverges for smaller $\vwO$.

{\bf AG perhaps it would be better to solve the implicit equation for
  rs/rsoi, and plot this in the top panel--assuming a fixed n of say
  1}. We may also compare our numerical results $r_{\rm s}/r_{\rm
  soi}$ an be compared directly to our analytic estimate in equation
\ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag}
shows the fractional difference between our numerical and analytic
results for $r_{\rm s}/r_{\rm soi}$.  The good agreement provides a
useful check of the numerical results.

%% AG: Describe conservation checks to additionally validate the results.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols represent $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies, while
    triangles correspond to cores. \emph{Bottom panel}: Fractional
    difference between our numerical calculation of $r_{\rm s}/r_{\rm
      soi}$ and the analytic result in
    equation~(\ref{eq:stag_analytic}). }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} Sources contributing to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it solid blue}), Ia supernovae ({\it dashed red}), millisecond pulsars ({\it solid orange}).  Each heating source varies with black hole mass $\Mbh$ due to the different average star formation history of galaxies of a given halo mass (see Appendix~\ref{app:windheat} for the detailed description).   We assume a stellar density power law slope of $\Gamma = 0.8$ in calculating $v_{w}^{\bullet \, 2}$ although the dependence on $\Gamma$ is weak {\bf BDM: just pick a value of Gamma!}.  The Ia heating rate is shown as a solid above the critical black hole mass for which $r_{\rm Ia} < r_{\rm s}$ (Fig.~\ref{fig:rs_rIa}), since this represents the condition for SN Ia to be well-approximated a continuously heating source. }
\end{figure}

>>>>

Figure~\ref{fig:stag} shows our results for the
stagnation radius $r_{\rm s}$, expressed in ratio to the radius of the
SMBH sphere of influence $r_{\rm soi}$, with different colors showing
different values of $v_{w}$.  Cusp and core galaxies are marked with
square and triangles, respectively.

 We may also compare our numerical results $r_{\rm s}/r_{\rm
  soi}$ an be compared directly to our analytic estimate in equation
\ref{eq:stag_analytic}.  The solid and dashed black curves in  Figure
\ref{fig:stag} show the analytic results for $r_{\rm s}/r_{\rm soi}$.
The good agreement provides a useful check of the numerical
results. Note that the analytic curves implicitly assume a density
slope, $n$ at $\rs$, which we have fixed to be 1 (0.5) for the solid
(dashed) curve. For small $\vw/\sigma$ this assumption breaks down.

For $\vw/\sigma \gg 1$ the value $\rs/\rinf$ does not depend on break
radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
have an effect. Notice that near where the solid analytic curve
diverges there are three green square, one over the other. These
points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
%% AG: Describe conservation checks to additionally validate the results.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols represent $v_{w} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies, while
    triangles correspond to cores. The black curves correspond to the
    analytic prediction from Equation~\eqref{stag_analytic}. The solid
    (dashed) curve is the correponds to $\Gamma=0.8$ and $n=1$
    ($\Gamma=0.1$ and $n=0.5$.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\emph Top Panel:}Sources contributing
  to the heating rate of the CNM, $\vwO$, including stellar wind
  heating ({\it orange}), Ia supernovae ({\it green}), millisecond
  pulsars ({\it blue}), and compton heating (\it pink).  Each heating
  source varies with black hole mass $\Mbh$ due to the different
  average star formation history of galaxies of a given halo mass (see
  Appendix~\ref{app:windheat} for the detailed description). The total
  heating rate is shown in black. To account for the non-steady nature
  of the Ia heating we multiply the Ia heating by $e^{-\rs/\rIa}$, so
  the contribution that the heating contribiution from Ia supernovae
  will be suppressed if the time between successive supernovae is much
  greater than the dynamical time at $\rs$. {\emph Bottom panel} The
  ratio of the heating ($\dot{q}_{\rm heat}$) to the cooling rate
  ($\dot{q}_{\rm cool}$) at $\rs$ from the total heating rate in the
  top panel. Above $\Mbh\simeq 5\times 10^7 \Msun$ $\dot{q}_{\rm
    heat}(\rs)<\dot{q}_{\rm cool}(\rs)$ and a thermal instability
  would arise. The thermally unstable region is marked in red in the
  bottom panel. All curves become dashed in the thermally unstable
  region of parameter space: we expect our model to break down in this
  regime as the steady-state assumption would be violated.}
\end{figure}
